Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-02 Report/convergence_centralized.tex
# WARNING: head commit changed in the meantime
updated Nam's response in the reviewer comments

\subsection{Uniqueness of the Beamformer Iterates}
The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without affecting the objective value. Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr},  while choosing the feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to begin the iterative procedure.

>>>>

\subsection{Uniqueness of the Beamformer Iterates}
The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without affecting the objective value. Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr},  while choosing a feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to initialize the iterative procedure.
